Follow-up Samples

### 2017-01-19 submission/manuscript_outline_20161024.tex
change model names in figs from init follow to before sample

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
for lesion and Initial and Follow up Models.} The shaded areas
represents the range of values of a 100 different 80/20 splits of the
test set data using either all variables (grey) or reduced variable
(red) models. The blue line represents the reduced variable model using
100\% of the data set. A) Lesion model. B) Initial/Follow up model

\textbf{Figure 4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Lesion and Initial Follow Up Reduced Variable Models} A)
Lesion positive probability adjustment of those with carcinoma from
initial to follow up sample B) Initial follow up positive probability
adjustment of those with carcinoma from initial to follow up sample C)
Lesion positive probability adjustment of those with adenoma as well as
those with SRN and the probability adjustment from initial to follow up
sample. D) Initial follow up positive probability adjustment of those
with adenoma as well as those with SRN and the probability adjustment
from initial to follow up sample. The dotted line represents the
threshold used to make the decision of whether a sample was positive or
not.

@@

\textbf{Figure S3: Summary of Important Variables in Initial Follow Up
Model} A) MDA of the most important variables in the lesion model. The
black point represents the median and the different colors are the
different runs up to 100. B) The total number of appearances of each
variable in the 100 different lesion models. The cutoff of 50\% was used
to assess importance.

\textbf{Figure S4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Lesion and Initial and Follow Up Full Variable Models} A)
Lesion positive probability adjustment of those with carcinoma from
initial to follow up sample B) Initial follow up positive probability
adjustment of those with carcinoma from initial to follow up sample C)
Lesion positive probability adjustment of those with adenoma as well as
those with SRN and the probability adjustment from initial to follow up
sample. D) Initial follow up positive probability adjustment of those
with adenoma as well as those with SRN and the probability adjustment
from initial to follow up sample. The dotted line represents the
threshold used to make the decision of whether a sample was positive or
not.

>>>>

\textbf{Figure 3: Graph of the Receiver Operating Characteristic Curve
for lesion and Before Sample Models.} The shaded areas represents the
range of values of a 100 different 80/20 splits of the test set data
using either all variables (grey) or reduced variable (red) models. The
blue line represents the reduced variable model using 100\% of the data
set. A) Lesion model. B) Defore sample model

\textbf{Figure 4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Lesion and Before Sample Reduced Variable Models} A) Lesion
positive probability adjustment of those with carcinoma from initial to
follow up sample B) Initial follow up positive probability adjustment of
those with carcinoma from initial to follow up sample C) Lesion positive
probability adjustment of those with adenoma as well as those with SRN
and the probability adjustment from initial to follow up sample. D)
Initial follow up positive probability adjustment of those with adenoma
as well as those with SRN and the probability adjustment from initial to
follow up sample. The dotted line represents the threshold used to make
the decision of whether a sample was positive or not.

@@

\textbf{Figure S3: Summary of Important Variables in Before Sample
Model} A) MDA of the most important variables in the lesion model. The
black point represents the median and the different colors are the
different runs up to 100. B) The total number of appearances of each
variable in the 100 different lesion models. The cutoff of 50\% was used
to assess importance.

\textbf{Figure S4: Breakdown by Carcinoma and Adenoma of Prediction
Results for Lesion and Before Sample Full Variable Models} A) Lesion
positive probability adjustment of those with carcinoma from initial to
follow up sample B) Initial follow up positive probability adjustment of
those with carcinoma from initial to follow up sample C) Lesion positive
probability adjustment of those with adenoma as well as those with SRN
and the probability adjustment from initial to follow up sample. D)
Initial follow up positive probability adjustment of those with adenoma
as well as those with SRN and the probability adjustment from initial to
follow up sample. The dotted line represents the threshold used to make
the decision of whether a sample was positive or not.
